IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/retrofit.tex

Existing language-based coarse-grained IFC
system~\cite{Hritcu:2013:YIB:2497621.2498098,stefan:2012:arxiv-flexible}
allow a sub-computation to temporarily raise the floating-label; after
the sub-computation is done, the floating-label is restored to its
original label. When this occurs, the enforcement mechanism must
ensure that information does not leak to the (less confidential)
program continuation. The presence of exceptions adds yet more
intricacies.  For instance, exceptions should not automatically
propagate from a sub-computation directly into the program
continuation, and, if such exceptions are allowed to be inspected, the
floating-label at the point of the exception-raise must be tracked
alongside the exception value~\cite{Hritcu:2013:YIB:2497621.2498098,
stefan:2012:arxiv-flexiblea, Hedin:2012}.  In contrast, our system
provides the same flexibility and guarantees with no extra checks: tasks
are used to execute sub-computations, but the mere definition of
isolated tasks guarantees that (a) tasks only transfer data to the
program continuation by using inter-task communication means, and (b)
exceptions do cross tasks boundaries automatically.

%% Here are two more examples of language features which have an
%% interesting interpretation when interpreted as task communication.
%% 
%% \paragraph{Stack frames versus scheduling}  One feature which is
%% supported by some information flow control systems is the ability to
%% temporarily raise the current label in order to do computation on data
%% (as done by LIO's |toLabeled| and Breeze's
%% brackets~\cite{Hritcu:2013:YIB:2497621.2498098,
%% stefan:2012:arxiv-flexible}).  After the computation, the label is lowered back to the original label,
%% enforcing a stack discipline.  When this occurs, care must be taken to ensure that information doesn't leak when
%% the label is lowered (e.g., the result must not be readable). In fact, systems with this feature generally only
%% achieve termination-insensitive non-interference: if the high secrecy
%% section doesn't terminate, this is observable by the non-execution of
%% the defunct public continuation.
%% 
%% When considering tasks, we will instead say that the allocation of a new
%% stack frame with a raised label corresponds to the creation of a new
%% isolated task; a sample encoding using our language is as follows:
%% \begin{align*}
%%     & |toLabeled l te @= | \\
%%     & |tab let i = taskId in| \\
%% %%    & |tab let j = TI (sandbox (IT (TI (setLabel l); TI (send i l (IT te)))))| \\
%%     & |tab let j = TI (sandbox (IT (TI (send i l (IT te)))))| \\
%%     & |tab in (\ _ . TI (setLabel l); TI (recvf x _ x unit))|
%% \end{align*}
%% There is one more ingredient: in a stack discipline, one generally
%% expects stack entries to be processed in order, rather than in parallel
%% as would be suggested by isolated tasks.  The sequential processing of
%% the task queue corresponds to a specific \emph{scheduling policy} of
%% these tasks.  In fact, the choice of scheduling here is the essential difference that
%% determines whether or not one can prove termination-insensitive or
%% termination-sensitive non-interference. We will show how different
%% scheduling policies give different security guarantees.
%% 
%% \paragraph{Exceptions versus message passing}
%% Another language feature that has caused difficulty for
%% many information flow control systems is exception handling
%% when built on top of this stack discipline.
%% %
%% The key difficulty appears when considering the propagation of exceptions
%% across stack boundaries where the current label is restored.
%% %
%% If the exception crosses this boundary, it can leak information about the
%% inner secret computation into a public computation; hence, one must
%% explicitly ensure that |toLabeled| does not propagate exceptions.
%% %
%% When stack frames are treated as isolated tasks, the correct semantics
%% are achieved automatically.
%% %
%% Exceptions simply stop when the hit the top-level of a task:
%% the only way for the frame to communicate information is by
%% initiating inter-task message passing.
%% %
%% For instance,
%% \begin{code}
%% TI(toLabeled l (IT (if te then fail else true))); true
%% \end{code}
%% always evaluates to |true|, regardless of the value of |te|.

@@

%
As in~\cite{Matthews:2007:OSM:1190216.1190220}, rules \textsc{T-border} and
\textsc{I-border} define the syntactic boundaries between the IFC and target
languages.
%
Intuitively, the boundaries respectively correspond to an upcall into and
downcall from the IFC runtime.
%
As an example, taking |targetLangML| as the target language, we can now define a
blocking receive (inefficiently) in terms of the asynchronous |recv| as series
of cross-language calls:
\begin{code}
  brecvf ix1 ix2 ie @=
  tab tab tab (IT (fix (\ k . TI (recvf ix1 ix2 ie (IT k)) )))
\end{code}

>>>>

Existing language-based, coarse-grained IFC
systems~\cite{Hritcu:2013:YIB:2497621.2498098,stefan:2012:arxiv-flexible}
allow a sub-computation to temporarily raise the floating-label; after
the sub-computation is done, the floating-label is restored to its
original label. When this occurs, the enforcement mechanism must
ensure that information does not leak to the (less confidential)
program continuation. The presence of exceptions adds yet more
intricacies.  For instance, exceptions should not automatically
propagate from a sub-computation directly into the program
continuation, and, if such exceptions are allowed to be inspected, the
floating-label at the point of the exception-raise must be tracked
alongside the exception value~\cite{Hritcu:2013:YIB:2497621.2498098,
stefan:2012:arxiv-flexiblea, Hedin:2012}.  In contrast, our system
provides the same flexibility and guarantees with no extra checks: tasks
are used to execute sub-computations, but the mere definition of
isolated tasks guarantees that (a) tasks only transfer data to the
program continuation by using inter-task communication means, and (b)
exceptions do cross tasks boundaries automatically.

@@

%
As in~\cite{Matthews:2007:OSM:1190216.1190220}, rules \textsc{T-border} and
\textsc{I-border} define the syntactic boundaries between the IFC and target
languages.
%
Intuitively, the boundaries respectively correspond to an upcall into and
downcall from the IFC runtime.
%
As an example, taking |targetLangML| as the target language, we can now define a
blocking receive (inefficiently) in terms of the asynchronous |recv| as series
of cross-language calls:
\begin{code}
brecvf ix1 ix2 ie @= (IT (fix (\ k . TI (recvf ix1 ix2 ie (IT k)) )))
\end{code}
